\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage{cmbright}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage[sf]{libertine}
\usepackage{microtype}
\usepackage{paracol}
\usepackage{supertabular}
\usepackage{titlesec}
\usepackage{changepage}
\hypersetup{colorlinks, urlcolor=black, linkcolor=black}

% Geometry
\geometry{hmargin=1.75cm, vmargin=0.5cm}
\columnratio{0.65, 0.35}
\setlength\columnsep{0.05\textwidth}
\setlength\parindent{0pt}
\setlength{\smallskipamount}{8pt plus 3pt minus 3pt}
\setlength{\medskipamount}{16pt plus 6pt minus 6pt}
\setlength{\bigskipamount}{24pt plus 8pt minus 8pt}

% Style
\pagestyle{empty}
\titleformat{\section}{\scshape\LARGE\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{\bigskipamount}{\smallskipamount}
\newcommand{\heading}[2]{\centering{\sffamily\Huge #1}\\\smallskip{\large{#2}}}
\newcommand{\entry}[4]{{{\textbf{#1}}} \hfill #3 \\ #2 \hfill #4}
\newcommand{\tableentry}[3]{\textsc{#1} & #2\expandafter\ifstrequal\expandafter{#3}{}{\\}{\\[6pt]}}

\begin{document}
	
	%\vspace*{\fill}
	
	\begin{paracol}{2}
		
		% Name & headline
		\heading{Anish Vempaty}{}
		
		\switchcolumn
		
		% Identity card
		\vspace{0.01\textheight}
		\begin{adjustwidth}{-31pt}{0pt}
		\begin{supertabular}{ll}
			\footnotesize\faPhone & +1 (929) 689-4564 \\
			\footnotesize\faEnvelope & \href{mailto:anish.vempaty@gmail.com}{anish.vempaty@gmail.com} \\
			\footnotesize\faLinkedin & \href{https://www.linkedin.com/in/anish-vempaty/}{linkedin.com/in/anish-vempaty/} \\
		\end{supertabular}
		\end{adjustwidth}
		
		\bigskip
		\switchcolumn*
		\vspace{-36pt}
		\section{Summary}
		\begin{flushleft}	
			Recent MS in Cybersecurity graduate from NYU with strong experience in backend development, cloud infrastructure, and system design. Proficient in building scalable, secure applications using AWS services, REST APIs, CI/CD pipelines, and containerized environments. Passionate about delivering clean, maintainable code and solving real-world engineering problems.
			\vspace{-16pt}
		\end{flushleft}
		\section{experience}
		
		\entry{SRMIST}{Data Engineer Intern}{Chennai, India}{Jun 2022 -- Dec 2022}
		\begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
			\item Developed automated web scraping tools to collect alumni data (Name, Phone, Address) from LinkedIn for graduates (1985–2015).
			\item Designed ETL pipeline to clean, extract, and organize large datasets for institutional outreach.
			\item Enhanced data collection efficiency by implementing robust error handling and batch processing.
		\end{itemize}
		\medskip
		\vspace{-20pt}
		
		\entry{Foxmula Corp}{Cybersecurity Engineer Intern}{Bengaluru, India}{Dec 2020 - Feb 2021}
		\begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
			\item Developed a Confidential Image Communication System combining chaos-based encryption with AES in Python, reducing encryption/decryption time by 10\%.
			\item Directed a team of 4 people to reduce time taken to encrypt and decrypt the image.
			\item Upgraded data processing pipelines using multithreading and efficient I/O handling in Python, improving data flow efficiency by 5\%.
		\end{itemize}
		
		\medskip
		\vspace{-20pt}
		
		\entry{Verzeo Tech}{AI Engineer Intern}{Bengaluru, India}{April 2020 - June 2020}
		\begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
			\item Engineered an application focusing on real time Traffic and Pedestrian Accident Detection using Python, OpenCV, and a YOLOv3-based object detection, increasing detection accuracy from 84\% to 93\% by fine-tuning model hyperparameters.
			\item Deployed the system with a Flask-based monitoring dashboard and implemented asynchronous logging to reduce system downtime by 5\%.
		\end{itemize}
		
		
		\switchcolumn
		\vspace{-36pt}
		\section{education}
		
		\entry{New York University}{MS, Cybersecurity}{NY, USA}{2023 -- 2025}
		\begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
			\item CGPA - 3.7 / 4
			\item \textbf{Awards}
			
			\begin{enumerate}
				\item \parbox{6cm} {\raggedright Volcano Project security self-assessment}
				\item NYU Scholarship
				\item Gyandhan Scholarship
			\end{enumerate}
			
		\end{itemize}
		
		\medskip
		
		\entry{SRMIST}{B.Tech, CSE}{Chennai, India}{2019 -- 2023}
		\begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
			\item CGPA - 9.27 / 10
		\end{itemize}
		
		%\switchcolumn
		
		\section{Skills}
		\begin{supertabular}{rl}
			
			\tableentry{\footnotesize\faRobot}{Python \textperiodcentered{} TensorFlow \textperiodcentered{} PyTorch \textperiodcentered{} }{}
			\tableentry{}{ Scikit-learn \textperiodcentered{} OpenCV \textperiodcentered{} MLflow}{}
			\tableentry{}{LangChain \textperiodcentered{} HuggingFace \textperiodcentered{} RAG \textperiodcentered{}}{}
			\tableentry{}{Airflow \textperiodcentered{} Reinforcement Learning \textperiodcentered{}}{}
			\tableentry{}{CNNs \textperiodcentered{} LSTMs \textperiodcentered{} NLP \textperiodcentered{} Deep Learning}{}
			\tableentry{}{Computer Vision \textperiodcentered{} Object Detection \textperiodcentered{}}{}
			\tableentry{}{Feature Extraction \textperiodcentered{} Edge ML \textperiodcentered{}}{}
			\tableentry{}{Raspberry Pi \textperiodcentered{} Sensor Input Handling}{}
			\tableentry{}{Real-Time Inference \textperiodcentered{} Model Tuning \textperiodcentered{}}{}
			\tableentry{}{LLMs \textperiodcentered{} GenAI \textperiodcentered{} Microcontrollers}{}
			
			\tableentry{\footnotesize\faCode}{Java \textperiodcentered{} C/C++ \textperiodcentered{} JavaScript \textperiodcentered{} SQL \textperiodcentered{} PHP}{}
			\tableentry{}{NoSQL \textperiodcentered{} Flask \textperiodcentered{} FastAPI \textperiodcentered{} REST APIs \textperiodcentered{}}{}
			\tableentry{}{Git \textperiodcentered{} Postman \textperiodcentered{} Docker \textperiodcentered{} Kubernetes \textperiodcentered{}}{}
			\tableentry{}{CI/CD \textperiodcentered{} Jenkins \textperiodcentered{} GitHub Actions}{}
			\tableentry{}{AWS \textperiodcentered{} System Design \textperiodcentered{} Debugging}{}
			\tableentry{}{Linux \textperiodcentered{} ARM \textperiodcentered{} x86 Architecture}{}
			\tableentry{}{BIOS \textperiodcentered{} Bootloading \textperiodcentered{} Kernel}{}
			
			
			\tableentry{\footnotesize\faLock}{Penetration Testing \textperiodcentered{} Threat Modeling \textperiodcentered{} Vulnerability Assessment}{}
			\tableentry{}{Vulnerability Assessment \textperiodcentered{} Metasploit \textperiodcentered{} Snort}{}
			\tableentry{}{Wireshark \textperiodcentered{} Burp Suite \textperiodcentered{} Nmap \textperiodcentered{} Snort}{}
			\tableentry{}{Cryptography \textperiodcentered{} Network Security \textperiodcentered{}}{}
			\tableentry{}{ RiskAssessment \textperiodcentered{} VPNs \textperiodcentered{} SIEM \textperiodcentered{} SOAR}{}
			\tableentry{}{MITRE ATT\&CK \textperiodcentered{} Cyber Kill Chain }{}
			\tableentry{}{Threat Hunting \textperiodcentered{} Threat Intelligence}{}
			\tableentry{}{SIEM (Splunk) \textperiodcentered{} DLP \textperiodcentered{} Access Control}{}
			\tableentry{}{Secure Boot \textperiodcentered{}  Embedded Linux \textperiodcentered{}}{}
			\tableentry{}{Logstash \textperiodcentered{} Gostash \textperiodcentered{} Chronicle }{}
			\tableentry{}{Scapy \textperiodcentered{}  Packet Analysis \textperiodcentered{} HSM}{}
			
			
			
			
			\tableentry{\footnotesize\faDatabase}{Data Engineering \textperiodcentered{} Data Pipelines \textperiodcentered{}}{}
			\tableentry{}{ETL \textperiodcentered{} Batch/Stream Processing}{}
			\tableentry{}{Apache Kafka \textperiodcentered{} Apache Spark \textperiodcentered{}}{}
			\tableentry{}{Hadoop \textperiodcentered{} HDFS \textperiodcentered{} Redshift \textperiodcentered{} BigQuery}{}
			\tableentry{}{Airflow \textperiodcentered{} SQL/NoSQL Optimization \textperiodcentered{}}{}
			\tableentry{}{Data Modeling \textperiodcentered{} Pandas}{}
			
			\tableentry{\footnotesize\faMobile}{Android Studio \textperiodcentered{}  Kotlin \textperiodcentered{} XML Layouts}{}
			\tableentry{}{RecyclerView \textperiodcentered{} Room DB \textperiodcentered{} Firebase \textperiodcentered{}}{}
			\tableentry{}{LiveData \textperiodcentered{} Jetpack Components}{}
			\tableentry{}{REST APIs \textperiodcentered{} UI Design}{}
			
			
		\end{supertabular}

		
		%\switchcolumn
		
		
		
		%		\section{other interests}
		%		\begin{supertabular}{rl}
			%			\tableentry{domain}{First Passion}{}
			%			\tableentry{}{Second Passion}{spaceafter}
			%			\tableentry{domain}{First Passion}{}
			%			\tableentry{}{Second Passion}{spaceafter}
			%		\end{supertabular}
		
		\bigskip
		%\newpage
		\section{certifications}
		{\raggedleft
		\begin{supertabular}{rl}
			\tableentry{2021}{\textbf{PadhAI Deep-Learning}}{}
			\tableentry{}{\href{https://padhai.onefourthlabs.in/certificates/fqthhgnrcu}{fqthhgnrcu}}{spaceafter}
			\tableentry{2021}{\textbf{\parbox{5cm}{\raggedright Microsoft Technology Associate (MTA):Security Fundamentals}}}{}
			\tableentry{}{\href{https://www.credly.com/badges/1e494a58-5cf7-405b-800a-14d980102870?source=linked_in_profile}{Credentials}}{spaceafter}
			\tableentry{2022}{\textbf{\parbox{5cm}{\raggedright Building Web Applications in PHP, University of Michigan }}}{}
			\tableentry{}{\href{https://www.coursera.org/account/accomplishments/verify/BXE45B434J2T}{BXE45B434J2T}}{spaceafter}
		\end{supertabular}
	}
		
		\switchcolumn
		\vspace{-16pt}
		
		\section{projects}
		\begin{flushleft}
			\entry{Edge Device Cyber Threat Detection Using ML}{}{}{}
			\vspace{-16pt}
			\begin{itemize}[noitemsep,topsep=0pt,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
				\item Built a smart security system using Python, Scapy, and Streamlit to detect cyber threats in real time by analyzing internet traffic.
				\item Trained classification models (Random Forest, SVM) on public datasets like CICIDS and NSL-KDD to distinguish malicious from benign traffic.
				\item Deployed the trained model on Raspberry Pi 5, enabling lightweight, on-device threat detection with low resource overhead.
				\item Used Scapy to capture internet packets and extract features, and Streamlit to build a live dashboard for monitoring threats visually.
				%\item Developed a Streamlit-based web dashboard to visualize threat logs and alerts, enhancing usability and system monitoring.
			\end{itemize}
			%\vspace{36pt}
		%	\newpage
			\entry{Cloud-Based Source Code Vulnerability Detector (AWS)}{}{}{}
			\vspace{-16pt}
			\begin{itemize}[noitemsep,topsep=0pt,leftmargin=3.5mm,rightmargin=0mm]
				\item Developed a cloud-native security tool to scan GitHub repos for vulnerabilities using Python and Semgrep, with optional AI remediation using Gemini.
				\item Designed a serverless architecture using AWS Lambda, SQS, SES, API Gateway, and DynamoDB to ensure scalability and async processing.
				\item Built a secure REST API to trigger scans, cache results by commit ID, and send AI-generated reports via email using SES.
				\item Implemented caching logic and decoupled remediation workflows using SQS queues and dual Lambda functions.
				\item Deployed a static frontend on S3 and integrated with API Gateway for real-time result viewing and scan submission.
			\end{itemize}
			
			\entry{3D Scene Reconstruction from Single Camera Video}{}{}{}
			\vspace{-16pt}
			\begin{itemize}[noitemsep,topsep=0pt,leftmargin=3.5mm,rightmargin=0mm]
				\item Implemented a 3D reconstruction pipeline from a single-camera input video using Python, COLMAP (Structure-from-Motion), and PyTorch.
				\item Extracted video frames using OpenCV and FFmpeg, processed them with COLMAP for camera pose estimation and sparse point cloud generation.
				\item Applied MiDaS/DPT-based monocular depth estimation and converted outputs into 3D point clouds.
				\item Generated photorealistic 3D scene representations using Neural Radiance Fields (NeRF), training with PyTorch.
				\item Visualized reconstructed 3D scenes in Python using Matplotlib and PyTorch3D, making the system interpretable even for non-technical users.
			\end{itemize}
			
		%	\entry{AI Chat Assistant App (Android)}{}{}{}
		%	\vspace{-16pt}
		%	\begin{itemize}[noitemsep,topsep=0pt,leftmargin=3.5mm,rightmargin=0mm]
		%		\item Developed a mobile chatbot app using Kotlin, Jetpack Compose, and Gemini API to generate real-time conversational responses.
		%		\item Built a clean Jetpack Compose UI with Material3 design and voice input/output using TTS and Speech-to-Text.
		%		\item Used Retrofit for secure API calls and Firestore to persist chat sessions and user messages.
		%		\item Enabled session-based context handling to support multi-turn conversations.
		%	\end{itemize}
			
			\entry{Volcano Project Security Self-Assessment}{}{}{}
			\vspace{-16pt}
			\begin{itemize}[noitemsep,topsep=0pt,leftmargin=3.5mm,rightmargin=0mm]
				\item Conducted a full security self-assessment on the Volcano CNCF project as part of NYU’s “Internet Security and Privacy” course.
				\item Followed CNCF Security Assessment Handbook and evaluated the project across three stages: threat modeling, code review, and deployment risks.
				\item Identified key security gaps, misconfigurations, and areas of improvement, delivering actionable mitigation strategies.
				\item Earned a merit-based scholarship for the quality and depth of the assessment report.
			\end{itemize}
			
			
			
		\end{flushleft}
		
		
	\end{paracol}
	
	%	\vspace*{\fill}
	
\end{document}